### 2024-10-13 draft-2/draft-2.tex
added contributors

\minor A \s{setoption} message is well-formed if it has a prefix of the form
⟨\ot\s{setoption name} {\it tok}\ot\sup+ \s{value}\ot⟩, where {\it tok}\ot\sup+
is one or more tokens (none of which are \s{value}) matching an option name
listed in an \s{option} message enqueued by the engine, and a suffix satisfying
the condition(s) for the corresponding option type:

@@

\vskip-0.5\parskip A \s{setoption} message is also well-formed if it is of the
form ⟨\ot\s{setoption name} {\it tok}\ot\sup+\pt⟩ where {\it tok}\ot\sup+ is one
or more tokens (none of which are \s{value}) matching an option name listed in
an \s{option} message enqueued by the engine for which the corresponding option
type is \s{button}.

>>>>

% TODO remember to note in the engine section that names and values cannot
%   contain “name” or “value”

\minor A \s{setoption} message is well-formed if it has a prefix of the form
⟨\ot\s{setoption name} {\it tok}\ot\sup+ \s{value}\ot⟩, where {\it tok}\ot\sup+
is one or more tokens matching an option name listed in an \s{option} message
enqueued by the engine, and a suffix satisfying the condition(s) for the
corresponding option type:

@@

\vskip-0.5\parskip A \s{setoption} message is also well-formed if it is of the
form ⟨\ot\s{setoption name} {\it tok}\ot\sup+\pt⟩ where {\it tok}\ot\sup+ is one
or more tokens matching an option name listed in an \s{option} message enqueued
by the engine for which the corresponding option type is \s{button}.
